Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-31 paper/paper_DEB.tex
Edited Sections 4 & 5.

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[JCDL '21]{JCDL '21: Joint Conference on
  Digital Libraries, September 27--30, 2021, Urbana--Champaign, Illinois, USA}
  \acmBooktitle{Joint Conference on Digital Libraries}
  %\acmPrice{1.00}
  %\acmISBN{911}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  %June 03--05, 2018, Woodstock, NY}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
\orcid{0002-1601-8729}
\author{Jane Greenberg}
\orcid{0001-7819-5360}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}
\author{Yasin Baki\c{s}}
\orcid{0001-6144-9440}
\author{Xiaojun Wang}
\orcid{0001-8639-6795}
\author{Henry Bart Jr.}
\orcid{0002-5662-9444}
\affiliation{
  \institution{Tulane University}
  \city{New Orleans}
  \state{Louisiana}
  \country{USA}
}
\author{David Breen}
\orcid{0002-1376-5008}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Wang, Bart and Breen}

@@

\section{Introduction}
Over the last several decades advances in computing and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain digital specimens. The U. S. National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of data and images for millions of biological specimens. These resources are globally available through a wide range of open access repositories, enabling researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
due to both image quality and metadata issues.
% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)

@@

\subsubsection{Threshold Adjustment}
The first calculation in the pixel analysis process determines the cutoff intensity between what constitutes the foreground (i.e.~the fish) and background of the image.
Initially, the calculation is based on the bounding box and mask generated by
\verb|detectron|. Specimen images are read in as gray scale, and pixels in the image are treated as unsigned integers between 0 and 255.
Otsu thresholding, a technique that maximizes the variance between the 
foreground and background intensities, is used to compute an initial cutoff value between foreground and background. 
While the Otsu value occasionally generates an accurate mask as is, usually
the contrast between foreground and background is low and much of the lighter parts of the fish (such as its tail fin) are marked as background.

@@

\subsubsection{Fallback} The pixel analysis process occasionally fails. This can occur if certain flood fill operations behave unexpectedly, or if the image is too washed out or otherwise atypical for the thresholding process to work correctly. In the event this happens, the original mask and bounding box generated by \verb|detectron| is used for metadata generation.
\subsection{Metadata Generation}
Including what has already been discussed, the following metadata properties are being currently being generated:

>>>>

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[JCDL '21]{JCDL '21: Joint Conference on
  Digital Libraries, September 27--30, 2021, Urbana--Champaign, Illinois, USA}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  %June 03--05, 2018, Woodstock, NY}
%\acmPrice{15.00}
%\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
\orcid{0002-1601-8729}
\author{Jane Greenberg}
\orcid{0001-7819-5360}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}
\author{Yasin Baki\c{s}}
\orcid{0001-6144-9440}
\author{Henry Bart Jr.}
\orcid{0002-5662-9444}
\affiliation{
  \institution{Tulane University}
  \city{New Orleans}
  \state{Louisiana}
  \country{USA}
}
\author{David Breen}
\orcid{0002-1376-5008}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Bart and Breen}

@@

\section{Introduction}

\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history. OR
Global access to natural history collections has accelerated over the last few decades to advances in cyberinfrastructure, digitization, and the general open science tenor}

Over the last several decades advances in computing, imaging, and
cyberinfrastructure have supported the growth of digital natural history collections; thus supporting the trends towards open scienc.
In the U.S., programs, such as the National Science Foundation’s former
Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of
data and images for millions of biological specimens. These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
due to both image quality and metadata issues.
% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)

@@

\subsubsection{Threshold Adjustment}
The first calculation in the pixel analysis process determines the cutoff intensity between what constitutes the foreground (i.e.~the fish) and background of the image.
Initially, the calculation is based on the bounding box and mask generated by
\verb|detectron|. Specimen images are read in as gray scale, and pixels in the image are treated as unsigned integers between 0 and 255.
Otsu thresholding \cite{Otsu1979ATS}, a technique that maximizes the variance between the 
foreground and background intensities, is used to compute an initial cutoff value between foreground and background. 
While the Otsu value occasionally generates an accurate mask as is, usually
the contrast between foreground and background is low and much of the lighter parts of the fish (such as its tail fin) are marked as background.

@@

\subsubsection{Fallback} The pixel analysis process occasionally fails,
e.g.~ flood-filling does not produce a large enough blob or
the bounding box adjustment does not terminate.
This can occur if certain flood fill operations behave unexpectedly, or if the image is too washed out or otherwise atypical for the thresholding process to work correctly. In the event this happens, the original mask and bounding box generated by \verb|detectron| is used for metadata generation.

\subsection{Metadata Generation}
Including what has already been discussed, the following metadata properties are being currently being generated:
